---
title: "Housing Price Analysis Appendix"
author: "Yangsu Roy Wang"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---
## 1) Import Data

Establish a housing price dataset by reading the excel data file and assign the contents to a variable `housing_prices`.

```{r echo=TRUE}
require(tidyverse)
require(readxl)
housing_prices <- read_excel("data/Housing_prices_revised.xlsx", col_types = c("numeric", "numeric", "numeric", 
                                           "numeric"))
```

## 2) Models and Statistics

a) Perform a multiple regression analysis to test whether house selling price can be effectively predicted by number of rooms and location.

```{r}
model <- lm(Selling.Price ~ Location + Number.of.Rooms, housing_prices)
summary(model)
```

b) Construct an ANOVA table using the aforementioned multiple regression analysis.

```{r}
anova(model)
```

c) Calculate the prediced selling price for a house with 9 rooms and is located in Dandenong.

```{r}
model$coefficients[1] + model$coefficients[2] * 0 + model$coefficients[3] * 9
```

d) Add a joint term between number of rooms and locations. Build a multiple regression model with interaction effects between two independent variables.

```{r}
model_joint <- lm(Selling.Price ~ Location + Number.of.Rooms + Location : Number.of.Rooms, housing_prices)
summary(model_joint)
```

## 3) Visualisation

a) Use a single linear regression model to find the relationship between house *selling price* and *number of rooms*. Plot the regression line. Differentiate the plots by properties in two different suburbs (Dandenong and Sunshine West) using different colour and shape.

```{r}
ggplot(housing_prices) +
  geom_point(size = 2.2, aes(x = Number.of.Rooms, y = Selling.Price, colour = as.factor(Location), 
             shape = as.factor(Location))) +
  geom_smooth(size = 0.7, aes(x = Number.of.Rooms, y = Selling.Price), method = lm, se = FALSE, 
              colour = "olivedrab4") +
  labs(title="1-1 Property prices in Dandenong and Sunshine West",
       subtitle = "Plot of effects by number of rooms and location",
       x="Number of Rooms", y = "Seling Price") +
  scale_shape_manual("Suburbs", values = c(19,17), labels = c("Dandenong", "Sunshine West")) +
  scale_colour_manual("Suburbs", values = c("salmon2","steelblue2"), labels = c("Dandenong", "Sunshine West")) +
  theme(plot.title = element_text(color = "#22292F", size = 12, face = "bold", hjust = 0.5),
        plot.subtitle = element_text(color = "#22292F", hjust = 0.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "#DAE1E7"), panel.grid.major.x = element_line(color = "#DAE1E7"),
        axis.line = element_line(color = "#3D4852"))
```

b) Use a simple boxplot to demonstrate effects of house prices differentiated by locations.

```{r}
ggplot(housing_prices) +
  geom_boxplot(aes(x = as.factor(Location), y = Selling.Price, fill = Location)) +
  labs(title="1-2 Property prices comparion between Dandenong and Sunshine West",
       x="Suburbs", y = "Seling Price") +
  theme(legend.position = "none", plot.title = element_text(color = "#22292F",size = 12, face = "bold",
        hjust = 0.5), plot.subtitle = element_text(hjust = 0.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "#DAE1E7"), panel.grid.major.x = element_line(color = "#DAE1E7"),
        axis.line = element_line(color = "#3D4852")) +
  scale_x_discrete(labels = c("0" = "Dandenong", "1" = "Sunshine West"))
```

c) Assign a new dataset `housing_prices_output` by adding columns *Predicted Price* and *Residuals*.

```{r}
housing_prices_output <- cbind(housing_prices)
housing_prices_output <- 
  housing_prices_output %>% 
  mutate("Predicted.Price" = model$fitted.values) %>% 
  mutate("Residuals" = model$residuals)
```

d) Create a residuals plot to check the pattern of residuals for the regression model.

```{r}
ggplot(housing_prices_output, aes(x = Predicted.Price, y = Residuals)) +
  geom_point(size = 2.2, aes(colour = "salmon2")) +
  geom_hline(yintercept = 0, color = "steelblue1") +
  labs(title="1-3 Residuals vs Fitted Value Plot", x = "Predicted Price", y = "Residuals") +
  theme(legend.position = "none", plot.title = element_text(color = "#22292F",size = 12, face = "bold",
        hjust = 0.5), panel.background = element_blank(), panel.grid.major = element_line(color = "#DAE1E7"),
        panel.grid.major.x = element_line(color = "#DAE1E7"), axis.line = element_line(color = "#3D4852"))
```

e) Create a Normal Quantile-Quantile (Q-Q) Plot to test the normality of the data residuals.

```{r}
ggplot(housing_prices_output, aes(sample = Residuals)) +
  stat_qq(aes(colour = "salmon2")) +
  stat_qq_line(aes(colour = "steelblue1")) +
  labs(title="1-4 Residuals Normal Q-Q Plot", y = "Residuals") +
  theme(legend.position = "none", plot.title = element_text(color = "#22292F",size = 12, face = "bold",
        hjust = 0.5), panel.background = element_blank(),
        panel.grid.major = element_line(color = "#DAE1E7"), panel.grid.major.x = element_line(color = "#DAE1E7"),
        axis.line = element_line(color = "#3D4852"))
```

